NMRlipids III: Lipid--Cholesterol Interactions in Atomistic Molecular Dynamics Simulations

### 2023-04-13 MANUSCRIPT/manuscript.tex
Update text

While the structure and dynamics of heterogeneous membranes are difficult to capture experimentally, atomistic resolution molecular dynamics (MD) simulations are widely used to provide a detailed view of complex membranes and the lateral organization of lipid bilayers driven by lipid--CHOL interactions \cite{rog14,rog2009ordering,berkowitz2009detailed,enkavi2019multiscale,marrink2019computational}. This is further facilitated by an increasing selection of available force fields with compatible lipid and protein parameters that enable simulations of complex membranes approaching realistic membrane mixtures.

>>>>

While the structure and dynamics of heterogeneous membranes are difficult to capture experimentally, atomistic resolution molecular dynamics (MD) simulations are widely used to provide a detailed view of complex membranes and the lateral organization of lipid bilayers driven by lipid--CHOL interactions \cite{rog14,rog2009ordering,berkowitz2009detailed,enkavi2019multiscale,marrink2019computational}. This is further facilitated by an increasing selection of available force fields with compatible lipid and protein parameters that enable the simulations of ever more complex and realistic membranes .
